---
title: "Cyptography Course Data Analysis"
author: "Joan Mwangi"
date: "7/3/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# **Online Cryptography Course Data Analysis**

## **Defining the Analytic Question**

Identify individuals most likely to click on her ads

## **Defining the metric of success**

Mapping out individuals most likely to click on the ad using different
visualization techniques and summary statistics,

## **Understanding the context**

A Kenyan entrepreneur has started an online cryptography course online
and would to identify individuals that are mostly likely to click on the
ads based on the data she collected a while back before posting in her
blog.

## **Recording the experimental design**

-   Loading the dataset

-   Cleaning the data

-   Performing necessary exploratory data analysis

-    Making conclusions and recommendations based on the findings
    gotten.

## **Data Relevance**

This dataset has relevant variables such as city, country, daily time
spent, daily internet usage, time stamp etc which will aid in giving
insights on the type of individual most likely to click on the ad.

------------------------------------------------------------------------

## **Loading the data**

```{r}
advertising <- read.csv("C:/Users/jojos/Downloads/advertising (2).csv")
#previewing the first  rows `r head(advertising)`
#Previewing the structure of the dataset 
#`r str(advertising)`
#Checking the number of rows and columns within the dataset 
#`r dim(advertising)`

```

## **Data Cleaning**

```{r}
#There are `r ColSums(is.na(advertising)) null values`
#There arg `r advertising[duplicated(advertising),] rows`
```

```{r}
names(advertising)[names(advertising) == "Male"] <- "Gender"
colnames(advertising)
```

```{r}
boxplot(advertising$Daily.Time.Spent.on.Site,advertising$Age,advertising$Area.Income)
```

\#Area income is the only column with outliers, however they will not be
dropped as the values below the interquartile range don't fall below 0,
thus essential in giving further insights in our data analysis.

# **Implementing the solution**

## **Univariate Analysis**

## Measures of Central Tendency

### Mean

```{r}
 mean(advertising$Daily.Time.Spent.on.Site)
mean(advertising$Age)
mean(advertising$Area.Income)
mean(advertising$Daily.Internet.Usage)
```

### Variance

```{r}
 var(advertising$Daily.Time.Spent.on.Site)
var(advertising$Age)
var(advertising$Area.Income)
var(advertising$Daily.Internet.Usage)
```

### Standard Deviation

```{r}
 sd(advertising$Daily.Time.Spent.on.Site)
sd(advertising$Age)
sd(advertising$Area.Income)
sd(advertising$Daily.Internet.Usage)
```

### Range

```{r}
 range(advertising$Daily.Time.Spent.on.Site)
range(advertising$Age)
range(advertising$Area.Income)
range(advertising$Daily.Internet.Usage)
```

\>The mean, variance, and standard deviations of the numerical columns:

-   Daily Time Spent on Site: Mean -- 65.0,standard
    deviation-15.85,variance - 251.33,range - 3.60,91.43

-   Age: Mean - 36, standard deviation - 8.79, variance-77.186, range -
    1961

-   Area Income: Mean- 55000, standard deviation - 13414.63, range-
    179952406,range - 13996.5

-   Internet Usage : Mean - 180, standard deviation - 4390, variance -
    19274.5, range- 104.78

### Bar plots

```{r}
barplot_clicked <- barplot(table(advertising$Clicked.on.Ad))
barplot_clicked
```

*The frequency distribution of individuals who clicked on the Ad are
equivalent with each category having 500.*

*From the bar plot, we can see that females were more with a frequency
distribution of 581 compared to males with 481.*

### Histograms

```{r}
 age_hist <- hist(advertising$Age)
```

```{r}
internetusage_hist <- hist(advertising$Daily.Internet.Usage)
internetusage_hist
###Majority of the individuals record an internet usage of above 150
```

```{r}
daily_time_hist <- hist(advertising$Daily.Time.Spent.on.Site)
daily_time_hist
#The graph is skewed to the right, with majority spending time more than 80
```

```{r}
 area_income_hist <- hist(advertising$Area.Income)
 area_income_hist
 #The graph is skewed to the left, with majority of the area income ranging from 5000 to 8000
```

### Quartiles

```{r}
quantile(advertising$Age)
quantile(advertising$Daily.Time.Spent.on.Site)
quantile(advertising$Area.Income)
quantile(advertising$Daily.Internet.Usage)
```

------------------------------------------------------------------------

## **Bi-variate Analysis**

### Correlation Matrix

```{r}
cor(advertising[,unlist(lapply(advertising,is.numeric))])
```

> From the correlation matrix we can deduce the following:

> Variables that are positively correlated are:
>
> -   Daily internet usage and age
> -   Clicked on ad and Age
> -   Daily time spent on the site and daily internet usage.
>
> Variables that are negatively correlated are:
>
> -   *Clicked on ad and daily internet usage*
>
> -   Age and daily internet usage
>
> -   Clicked on Ad and area income
>
> -   Age and daily time spent on site

### Loading the tidyverese library to the environment

```{r}
library(tidyverse)
```

```{r}
ggplot(data=advertising) + geom_boxplot(mapping=aes(x=reorder(x=Clicked.on.Ad,Daily.Time.Spent.on.Site,FUN=median),y=Daily.Time.Spent.on.Site))+ coord_flip()
```

*plotting a box plot to show the relationship between daily time spent
on the ads and clicking on ad*

*The distribution of the time spent on the site around 45 and 90 are
individuals that didn't click on the ad which is higher than those that
actually clicked on the ad with a distribution of around 30 and 90.*

### Scatter plots

```{r}
plot(advertising$Daily.Internet.Usage, advertising$Clicked.on.Ad, xlab="Daily Internet Usage", ylab="Clicked.on.Ad")

```

*From the scatter,majority of the individuals that clicked on the ad
spent less daily internet usage with values ranging from 100 and 150
compared to those that had ample internet usage of 200 to 250*

```{r}
plot(advertising$Daily.Time.Spent.on.Site, advertising$Clicked.on.Ad, xlab="Daily time spent on site", ylab="Clicked.on.Ad")

```

*Just as seen in the scatter plot for daily internet usage, individuals
that spend less time on the site are more likely to click on the ad with
time less than 40 compared to those that spent more time on the site
with majority ranging from 70 to 80*

```{r}
plot(advertising$Area.Income, advertising$Clicked.on.Ad, xlab="Area Income", ylab="Clicked.on.Ad")

```

*Individuals with an area income of around 5000 and 7500 didn't click on
the ad, however this cannot be clearly stated for those that did click
on the ad.*

```{r}
plot(advertising$Age, advertising$Clicked.on.Ad, xlab="Age", ylab="Clicked.on.Ad")

```

*individuals that are 20 to 50 are more likely not to click on the ad,
however it is unclear on the age for those that actually clicked on the
ad.*

*The distribution of the time spent on the site around 45 and 90 are
individuals that didn't click on the ad which is higher than those that
actually clicked on the ad with a distribution of around 30 and 90.*

```{r}
plot(advertising$Age, advertising$Daily.Time.Spent.on.Site, xlab="Age", ylab="Daily Time Spent on Site")
```

# Conclusion

> Based on the analysis:

-   When consumers spend more on internet usage doesn't necessary mean
    that they will click on the ad

-   When time spent on the ad is less than 30 they are more likely to
    click on the ad compared to those that spent a long time on the
    internet

-    The higher the area income the lower the chances an individual will
    click on the ad

# Recommendation

I would recommend that the ads should target individuals whose area
income range from 3000, has spent less than 40 units on the internet
which could prompt the potential client to click on the ad, and less
internet usage(less than 150). Intuitively, this makes sense as
individuals that spend less time both on usage and time might have
garnered interest probably if it was the first ad they came across or
were briefly browsing the net and the ad suddenly popped up. Targeting
older people (50 and above) as seen from the correlation matrix, are
more likely to spend less time on the site.
